### 2021-01-28 input/proposal.tex
nixos file + general idea

>>>>

The main idea is maintaining graphs of partitions using local
knowledge only and use graphs as often as possible: it improves
resilience to crashes, convergence speed etc. Unfortunately,
maintaining graphs of partitions in dynamic networks may require the
use of broadcast tree. The removal of a communication channel between
2 processes may remove an advantageous path from processes downstream
to the source of the partition they belong to.
